---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

# Creating the environment

```{r}
library(tidyverse)
library(tosr)
library(bibliometrix)
library(lubridate)
library(igraph)
library(tidytext)
library(wordcloud)
library(rebus)
library(ggrepel) # improve donut visualization
```

# Data getting

```{r}
wos_scopus_tos <- 
  tosr::tosr_load("DCA 467 15 July 2021.bib",  # Create data from searches 
                  "DCA 467 15 July 2021.txt")

tree_of_science <- 
  tosr::tosR("DCA 467 15 July 2021.bib",  # Create data from searches 
             "DCA 467 15 July 2021.txt")

wos <- 
  bibliometrix::convert2df("DCA 467 15 July 2021.txt") # create dataframe from wos file

scopus <- 
  bibliometrix::convert2df("DCA 467 15 July 2021.bib", # Create dataframe from scopus file
                           dbsource = "scopus", 
                           format = "bibtex")


```

## Table 1. Search Criteria

```{r}
table_1 <- 
  tibble(wos = length(wos$SR), # Create a dataframe with the values.
         scopus = length(scopus$SR), 
         total = length(wos_scopus_tos$df$SR))
table_1
```

## Figure 1. Languages

```{r}
main_languages <- 
  wos_scopus_tos$df |> 
  select(LA) |> 
  separate_rows(LA, sep = "; ") |> 
  count(LA, sort = TRUE) |> 
  slice(1:5)

other_languages <- 
  wos_scopus_tos$df |> 
  separate_rows(LA, sep = "; ") |> 
  select(LA) |> 
  count(LA, sort = TRUE) |> 
  slice(6:n) |> 
  summarise(n = sum(n)) |> 
  mutate(LA = "OTHERS") |> 
  select(LA, n)

languages <- 
  main_languages |> 
  bind_rows(other_languages) |> 
  mutate(percentage = n / sum(n),
         percentage = round(percentage, 
                            digits = 2) ) |> 
  rename(language = LA) |>
  select(language, percentage, count = n)

languages
```


```{r}
df <- languages |> 
  rename(value = percentage, group = language) |>
  mutate(value = value * 100) |> 
  select(value, group)

df2 <- df %>% 
  mutate(csum = rev(cumsum(rev(value))), 
         pos = value/2 + lead(csum, 1),
         pos = if_else(is.na(pos), value/2, pos))

ggplot(df, aes(x = 2 , y = value, fill = fct_inorder(group))) +
  geom_col(width = 1, color = 1) +
  coord_polar(theta = "y") +
  geom_label_repel(data = df2,
                   aes(y = pos, label = paste0(value, "%")),
                   size = 4.5, nudge_x = 1, show.legend = FALSE) +
   theme(panel.background = element_blank(),
        axis.line = element_blank(), 
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        plot.title = element_text(hjust = 0.5, size = 18)) +
  labs(title = "Languages") +
  guides(fill = guide_legend(title = "")) +
  theme_void() +
  xlim(0.5, 2.5)
```

## Figure 2. Scientific Production

```{r}
wos_anual_production <- 
  wos |> 
  select(PY) |> 
  count(PY, sort = TRUE) |> 
  na.omit() |> 
  filter(PY >= 2000,
         PY < year(today())) |> 
  mutate(ref_type = "wos")

scopus_anual_production  <- 
  scopus |> 
  select(PY) |> 
  count(PY, sort = TRUE) |> 
  na.omit() |> 
  filter(PY >= 2000,
         PY < year(today())) |>
  mutate(ref_type = "scopus")

total_anual_production <- 
  wos_scopus_tos$df |> 
  select(PY) |> 
  count(PY, sort = TRUE) |> 
  na.omit() |> 
  filter(PY >= 2000,
         PY < year(today())) |>
  mutate(ref_type = "total")

wos_scopus_total_annual_production <- 
  wos_anual_production |> 
  bind_rows(scopus_anual_production,
            total_anual_production) 

figure_2_data <- 
  wos_scopus_total_annual_production |> 
  mutate(PY = replace_na(PY, replace = 0)) |> 
  pivot_wider(names_from = ref_type, 
              values_from = n) |> 
  arrange(desc(PY))

figure_2_data 
```

```{r}
wos_scopus_total_annual_production |> 
  ggplot(aes(x = PY, y = n, color = ref_type)) +
  geom_line() +
  labs(title = "Annual Scientific Production", 
       x = "years",
       y = "papers") +
  theme(plot.title = element_text(hjust = 0.5)) 
```

## Table 2. Country production

```{r}
data_biblio_wos <- biblioAnalysis(wos)

wos_country <- 
  data_biblio_wos$Countries |> 
  data.frame() |> 
  mutate(database = "wos") |> 
  select(country = Tab, papers = Freq, database ) |> 
  arrange(desc(papers)) 

data_biblio_scopus <- biblioAnalysis(scopus)

scopus_country <- 
  data_biblio_scopus$Countries |> 
  data.frame() |> 
  mutate(database = "scopus") |> 
  select(country = Tab, papers = Freq, database ) |> 
  arrange(desc(papers)) 

data_biblio_total <- biblioAnalysis(wos_scopus_tos$df)
  
total_country <- 
  data_biblio_total$Countries |> 
  data.frame() |> 
  mutate(database = "total") |> 
  select(country = Tab, papers = Freq, database ) |> 
  arrange(desc(papers)) 

wos_scopus_total_country <- 
  wos_country |> 
  bind_rows(scopus_country, 
            total_country) |> 
  mutate(country = as.character(country)) |> 
  pivot_wider(names_from = database, 
              values_from = papers) |> 
  arrange(desc(total)) |> 
  slice(1:10) |> 
  mutate(percentage = total / (table_1 |> pull(total)),
         percentage = round(percentage, digits = 2))

wos_scopus_total_country
```

## Table 3. Author production

```{r}
wos_authors <- 
  data_biblio_wos$Authors |> 
  data.frame() |> 
  rename(authors_wos = AU, papers_wos = Freq) |> 
  arrange(desc(papers_wos)) |> 
  slice(1:10) |> 
  mutate(database_wos = "wos")


scopus_authors <- 
  data_biblio_scopus$Authors |> 
  data.frame() |> 
  rename(authors_scopus = AU, papers_scopus = Freq) |> 
  arrange(desc(papers_scopus)) |> 
  slice(1:10) |> 
  mutate(database_scopus = "scopus")

total_authors <- 
  data_biblio_total$Authors |> 
  data.frame() |> 
  rename(authors_total = AU, 
         papers_total = Freq) |> 
  arrange(desc(papers_total)) |> 
  slice(1:10) |> 
  mutate(database_total = "total")

wos_scopus_authors <- 
  wos_authors |> 
  bind_cols(scopus_authors,
            total_authors)

wos_scopus_authors
```

## Table 4. Journal production

```{r}
wos_journal <- 
  wos |> 
  filter(str_detect(DT, "ARTICLE")) |> 
  select(journal = SO) |> 
  na.omit() |> 
  count(journal, sort = TRUE) |> 
  slice(1:20) |> 
  rename(publications = n) |> 
  mutate(database = "wos")

scopus_journal <- 
  scopus |> 
  filter(str_detect(DT, "ARTICLE")) |> 
  select(journal = SO) |> 
  na.omit() |> 
  count(journal, sort = TRUE) |> 
  slice(1:20) |> 
  rename(publications = n) |> 
  mutate(database = "scopus")

total_journal <- 
  wos_scopus_tos$df |> 
  filter(str_detect(DT, "ARTICLE")) |> 
  select(journal = SO) |> 
  na.omit() |> 
  count(journal, sort = TRUE) |> 
  slice(1:20) |> 
  rename(publications = n) |> 
  mutate(database = "total")

wos_scopus_total_journal <- 
  wos_journal |> 
  bind_rows(scopus_journal, 
            total_journal) |> 
  pivot_wider(names_from = database, 
              values_from = publications) |> 
  arrange(desc(total)) |> 
  slice(1:10) |> 
  mutate(percentage = total / table_1 |> pull(total),
         percentage = round(percentage, digits = 2))


wos_scopus_total_journal
```

## Figure 3. Co-citation network

### Author co-citation network

```{r}
wos_scopus_author_metatag <- 
  metaTagExtraction(wos_scopus_tos$df, Field = "CR_AU")

wos_scopus_author_co_citation_matrix <- 
  biblioNetwork(M = wos_scopus_author_metatag, 
                analysis = "co-citation", 
                network = "authors")

plot_net_author_co_citation <- 
  networkPlot(wos_scopus_author_co_citation_matrix, 
              weighted=T, 
              n = 30, 
              Title = "Author Co-citation Network", 
              type = "fruchterman", 
              size=T,
              edgesize = 5,
              labelsize=0.7)
```

### Author Collaboration network

```{r}
wos_scopus_author_collab_matrix <- 
  biblioNetwork(M = wos_scopus_tos$df, 
                analysis = "collaboration", 
                network = "authors")

plot_author_collab <- 
  networkPlot(NetMatrix = wos_scopus_author_collab_matrix, 
              weighted=T, n = 30, 
              Title = "Author Collaboration Network", 
              type = "fruchterman", 
              size=T,
              edgesize = 5,
              labelsize=0.7)
```

### Country Collaboration Network

```{r}
wos_scopus_country_collab_matrix <- 
  biblioNetwork(M = wos_scopus_tos$df, 
                analysis = "collaboration", 
                network = "countries")

plot_country_collab <- 
  networkPlot(wos_scopus_country_collab_matrix, 
              weighted=T, n = 30, 
              Title = "Country Collaboration Network", 
              type = "fruchterman", 
              size=T,
              edgesize = 5,
              labelsize=0.7)
```

### Keyword co-citation network

```{r}
wos_scopus_keyword_co_occurrence_matrix <- 
  biblioNetwork(M = wos_scopus_tos$df, 
                analysis = "co-occurrences", 
                network = "keywords", 
                sep = ";")

plot_net_co_occurrence <- 
  networkPlot(wos_scopus_keyword_co_occurrence_matrix, 
              weighted=T, n = 30, 
              Title = "Keyword Co-occurrence Network", 
              type = "fruchterman", 
              size=T,
              edgesize = 5,
              labelsize=0.7)
```

## Figure 4. Tree of Science

### Tree of Science

```{r}
tree_of_science
```

### Clustering analysis

Finding the clusters

```{r}
nodes <-  
  tibble(name = V(wos_scopus_tos$graph)$name) |> 
  left_join(wos_scopus_tos$nodes, 
            by = c("name" = "ID_TOS"))

wos_scopus_citation_network_1 <- 
  wos_scopus_tos$graph |> 
  igraph::set.vertex.attribute(name = "full_name", 
                               index = V(wos_scopus_tos$graph)$name, 
                               value = nodes$CITE)

nodes_1 <- 
  tibble(name = V(wos_scopus_citation_network_1)$name,
         cluster = V(wos_scopus_citation_network_1)$subfield,
         full_name = V(wos_scopus_citation_network_1)$full_name)
  
nodes_2 <- 
  nodes_1 |> 
  count(cluster, sort = TRUE) |> 
  mutate(cluster_1 = row_number()) |> 
  select(cluster, cluster_1)

nodes_3 <- 
  nodes_1 |> 
  left_join(nodes_2) |> 
  rename(subfield = cluster_1) |> 
  select(name, full_name, subfield)

edge_list <- 
  get.edgelist(wos_scopus_citation_network_1) |> 
  data.frame() |> 
  rename(Source = X1, Target = X2)

wos_scopus_citation_network <- 
  graph.data.frame(d = edge_list, 
                   directed = FALSE, 
                   vertices = nodes_3)

wos_scopus_citation_network |> 
  summary()
```

Choosing clusters

```{r}
clusters <- 
  tibble(cluster = V(wos_scopus_citation_network)$subfield) |> 
  count(cluster, sort = TRUE)

clusters |> 
  ggplot(aes(x = reorder(cluster, n), y = n)) +
  geom_point() 
```

Removing not chosen clusters

```{r}
wos_scopus_citation_network_clusters <- 
  wos_scopus_citation_network |> 
  delete.vertices(which(V(wos_scopus_citation_network)$subfield != 1 & # filter clusters 
                          V(wos_scopus_citation_network)$subfield != 2 &
                          V(wos_scopus_citation_network)$subfield != 3  &
                          V(wos_scopus_citation_network)$subfield != 4))

wos_scopus_citation_network_clusters |> 
  summary()
```

### Cluster 1

```{r}
pal <- brewer.pal(8,"Dark2")

nodes_full_data <- 
  tibble(name = V(wos_scopus_citation_network)$name,
         cluster = V(wos_scopus_citation_network)$subfield,
         full_name = V(wos_scopus_citation_network)$full_name)

cluster_1 <- 
  wos_scopus_citation_network |> 
  delete.vertices(which(V(wos_scopus_citation_network)$subfield != 1))

cluster_1_page_rank <- 
  cluster_1 |> 
  set.vertex.attribute(name = "page_rank", 
                       value = page_rank(cluster_1)$vector)

cluster_1_df <- 
  tibble(name = V(cluster_1_page_rank)$name,
         full_name = V(cluster_1_page_rank)$full_name,
         page_rank = V(cluster_1_page_rank)$page_rank,
         cluster = V(cluster_1_page_rank)$subfield,)

nodes_full_data |> 
  filter(cluster == 1) |> 
  select(full_name) |> 
  mutate(full_name = str_extract(full_name, SPC %R%  # Regular expressions 
                                   one_or_more(WRD) %R% 
                                   SPC %R% 
                                   one_or_more(or(WRD, ANY_CHAR))),
         full_name = str_remove(full_name, OPEN_PAREN %R% 
                                  repeated(DGT, 4) %R% 
                                  CLOSE_PAREN %R%
                                  one_or_more(or(WRD,ANY_CHAR))),
         full_name = str_trim(full_name))  |> 
  unnest_tokens(output = word, input = full_name) |> # Tokenization
  anti_join(stop_words) |>  # Removing stop words
   filter(word != "doi",
         !str_detect(word, "[0-9]")) |>  # WoS data
  filter(word == str_remove(word, pattern = "citation"),
         word == str_remove(word, pattern = "research"),  # Words removed
         word == str_remove(word, pattern = "analysis"), 
         word == str_remove(word, pattern = "science"),
         word == str_remove(word, pattern = "scientometric"),
         word == str_remove(word, pattern = "bibliometric")) |>
  count(word, sort = TRUE) |> 
  with(wordcloud(word, 
                 n, 
                 random.order = FALSE, 
                 max.words = 50, 
                 colors=pal))
```

### Cluster 2

```{r}
cluster_2 <- 
  wos_scopus_citation_network |> 
  delete.vertices(which(V(wos_scopus_citation_network)$subfield != 2))

cluster_2_page_rank <- 
  cluster_2 |> 
  set.vertex.attribute(name = "page_rank", 
                       value = page_rank(cluster_2)$vector)

cluster_2_df <- 
  tibble(name = V(cluster_2_page_rank)$name,
         full_name = V(cluster_2_page_rank)$full_name,
         page_rank = V(cluster_2_page_rank)$page_rank,
         cluster = V(cluster_2_page_rank)$subfield,)

nodes_full_data |> 
  filter(cluster == 2) |> 
  select(full_name) |> 
  mutate(full_name = str_extract(full_name, SPC %R%  # Regular expressions 
                                   one_or_more(WRD) %R% 
                                   SPC %R% 
                                   one_or_more(or(WRD, ANY_CHAR))),
         full_name = str_remove(full_name, OPEN_PAREN %R% 
                                  repeated(DGT, 4) %R% 
                                  CLOSE_PAREN %R%
                                  one_or_more(or(WRD,ANY_CHAR))),
         full_name = str_trim(full_name))  |> 
  unnest_tokens(output = word, input = full_name) |> 
  anti_join(stop_words) |>
  filter(word != "doi",
         !str_detect(word, "[0-9]")) |>  # WoS data
  filter(word == str_remove(word, pattern = "citation"),
         word == str_remove(word, pattern = "research"), 
         word == str_remove(word, pattern = "analysis"), 
         word == str_remove(word, pattern = "science"),
         word == str_remove(word, pattern = "scientometric"),
         word == str_remove(word, pattern = "bibliometric")) |>
  count(word, sort = TRUE) |> 
  with(wordcloud(word, 
                 n, 
                 random.order = FALSE, 
                 max.words = 50, 
                 colors=pal))
```

### Cluster 3

```{r}

cluster_3 <- 
  wos_scopus_citation_network |> 
  delete.vertices(which(V(wos_scopus_citation_network)$subfield != 3))

cluster_3_page_rank <- 
  cluster_3 |> 
  set.vertex.attribute(name = "page_rank", 
                       value = page_rank(cluster_3)$vector)

cluster_3_df <- 
  tibble(name = V(cluster_3_page_rank)$name,
         full_name = V(cluster_3_page_rank)$full_name,
         page_rank = V(cluster_3_page_rank)$page_rank,
         cluster = V(cluster_3_page_rank)$subfield,)

nodes_full_data |> 
  filter(cluster == 3) |> 
  select(full_name) |> 
  mutate(full_name = str_extract(full_name, SPC %R%  # Regular expressions 
                                   one_or_more(WRD) %R% 
                                   SPC %R% 
                                   one_or_more(or(WRD, ANY_CHAR))),
         full_name = str_remove(full_name, OPEN_PAREN %R% 
                                  repeated(DGT, 4) %R% 
                                  CLOSE_PAREN %R%
                                  one_or_more(or(WRD,ANY_CHAR))),
         full_name = str_trim(full_name))  |> 
  unnest_tokens(output = word, input = full_name) |> 
  anti_join(stop_words) |>
   filter(word != "doi",
         !str_detect(word, "[0-9]")) |>  # WoS data 
  filter(word == str_remove(word, pattern = "citation"),
         word == str_remove(word, pattern = "research"), 
         word == str_remove(word, pattern = "analysis"), 
         word == str_remove(word, pattern = "science"),
         word == str_remove(word, pattern = "scientometric"),
         word == str_remove(word, pattern = "bibliometric")) |>
  count(word, sort = TRUE) |> 
  with(wordcloud(word, 
                 n, 
                 random.order = FALSE, 
                 max.words = 50, 
                 colors=pal))
```
### Cluster 4

```{r}

cluster_4 <- 
  wos_scopus_citation_network |> 
  delete.vertices(which(V(wos_scopus_citation_network)$subfield != 4))

cluster_4_page_rank <- 
  cluster_4 |> 
  set.vertex.attribute(name = "page_rank", 
                       value = page_rank(cluster_4)$vector)

cluster_4_df <- 
  tibble(name = V(cluster_4_page_rank)$name,
         full_name = V(cluster_4_page_rank)$full_name,
         page_rank = V(cluster_4_page_rank)$page_rank,
         cluster = V(cluster_4_page_rank)$subfield,)

nodes_full_data |> 
  filter(cluster == 4) |> 
  select(full_name) |> 
  mutate(full_name = str_extract(full_name, SPC %R%  # Regular expressions 
                                   one_or_more(WRD) %R% 
                                   SPC %R% 
                                   one_or_more(or(WRD, ANY_CHAR))),
         full_name = str_remove(full_name, OPEN_PAREN %R% 
                                  repeated(DGT, 4) %R% 
                                  CLOSE_PAREN %R%
                                  one_or_more(or(WRD,ANY_CHAR))),
         full_name = str_trim(full_name))  |> 
  unnest_tokens(output = word, input = full_name) |> 
  anti_join(stop_words) |> 
   filter(word != "doi",
         !str_detect(word, "[0-9]")) |>  # WoS data
  filter(word == str_remove(word, pattern = "citation"),
         word == str_remove(word, pattern = "research"), 
         word == str_remove(word, pattern = "analysis"), 
         word == str_remove(word, pattern = "science"),
         word == str_remove(word, pattern = "scientometric"),
         word == str_remove(word, pattern = "res")) |>
  count(word, sort = TRUE) |> 
  with(wordcloud(word, 
                 n, 
                 random.order = FALSE, 
                 max.words = 50, 
                 colors=pal))
```

# Exporting files

```{r}

write_csv(table_1, "table_1.csv") # Exporting table 1
write_csv(wos_scopus_total_country, "table_2_.csv")  # Exporting table 2
write_csv(wos_scopus_authors, "table_3.csv") # Exporting table 3
write_csv(wos_scopus_total_journal, "table_4.csv") # Exporting table 4


write_csv(languages, "figure_1.csv") # Exporting data figure 1 
write_csv(figure_2_data, "figure_2.csv") # Exporting data figure 2

write.graph(wos_scopus_tos$graph, "citation_network_full.csv", "graphml") # Exporting graph
write.graph(wos_scopus_citation_network_clusters, 
            "wos_scopus_citation_network_clusters.graphml", 
            "graphml")

write.csv(tree_of_science, "tree_of_science.csv") # Exporting Tree of Science

write.csv(cluster_1_df, "cluster_1.csv") # Exporting cluster 1
write.csv(cluster_2_df, "cluster_2.csv") # Exporting cluster 2
write.csv(cluster_3_df, "cluster_3.csv") # Exporting cluster 3
write.csv(cluster_4_df, "cluster_4.csv") # Exporting cluster 4

write.csv(nodes_full_data, "nodes_full_data.csv") # Exporting all nodes
```

